\section{Bootstrap}
Sample uniform from data points with replacement, compute bootstrapped estimator. For a large dataset $x_1, ..., x_n$ the probability that $x_1$ is contained in a random bootstrap dataset is: \\
$1-(1-1/n)^n \approx 2/3$ (for large $n$, limit goes to $1-1/e$).
\subsection*{Bootstrap Consistency}
For an increasing sequence $a_n$ (often $\sqrt{n}$) where $a_n^{-1}$ is the convergence rate of $\hat \theta_n$:
$\mathbb{P}(a_n(\hat \theta_n - \theta) \leq x) - \mathbb{P}^*(a_n(\hat \theta_n^* - \hat \theta_n) \leq x) \to^P 0$ as $n\to \infty$. This holds when $\sqrt{n}(\hat \theta_n - \theta)$ is asympt. normal. Allows to estimate $\text{Bias}(\hat \theta_n) = E[\hat \theta_n] - \theta$ by $E^*[\hat \theta^*_n] - \hat \theta_n$. Can also estimate $\text{Var}^*(\hat\theta_n)$ by $\text{Var}^*(\hat\theta^*_n)$ .
\subsection*{Bootstrap CI}
\textbf{Reversed Quantile CI:} (intelligent) $[\hat \theta_n - q_{\hat \theta^* - \hat \theta}(1- \alpha / 2), \hat \theta_n - q_{\hat \theta^* - \hat \theta}(\alpha / 2)]$ \textcolor{red}{(type="basic")}\\
\textbf{Normal Bootstrap CI:} Assume $\hat\theta_n$ to be asympt. normal: $\hat\theta_n \pm q_z(1-\alpha / 2)\hat{sd}(\hat\theta_n)$ where $z \sim \mathcal{N}(0,1)$ and $\hat{sd}(\hat\theta_n)=\sqrt {{\text{Var}(\hat\theta_n^*)}}$ \textcolor{red}{(type="norm")}\\ \textbf{Quantile Bootstrap CI:} (naive) not theoret. justified unless $\hat\theta_n$ is symm.:
$[q_{\theta_n^*}(\alpha / 2), q_{\theta_n^*}(1-\alpha / 2)]$ \textcolor{red}{(type="perc")}. Same as \textit{reversed quantile bootstrap CI} if $\hat\theta_n^* - \hat\theta_n$ is symm. around 0,\\ 
\textbf{Double bootstrap CI:} After we have a CI $I_\alpha$, we use a 2nd bootstrap estimate a $h(\alpha)\,s.t.\,\mathbb{P}(I_\alpha\hat\theta_n-\theta \ni \hat\theta_n-\theta) = 1-h(\alpha)$. Then we choose $\alpha'$ s.t. $h(\alpha')=\alpha$. Algo: 1) for each bootstrap iteration we take our bootstrap data and we run another round of bootstrap on that data to check weather the $\hat\theta^*$ fits in the CI. $h(\alpha)$ is the ratio of bootstrap iteration for which it fits inside\\
\textbf{Parametric Bootstrap:} We assume $X_1\dots X_n \sim P_\theta$. We estimate $\hat\theta$ then we draw bootstraps $X_1^*\dots X_n^*\sim P_{\hat\theta}$. More precise if the assumption is correct\\
\textbf{Regression bootstrap:} 
We do $Y_i^* = \hat m(x_i) + \epsilon_i$
\textbf{parametric:} 
$\epsilon_i \sim \mathcal{N}(0, \hat\sigma^2)$
\textbf{model-based:} 
$\epsilon_i \sim \hat P_{r}$, the empirical dist. of residuals
\begin{codebox}{r}{Bootstrap}
library(boot)
sample(c(1:n), n, replace=T) # bootstrap sample
# f statistics with args: (x, ind)
res.boot <- boot(data, f, R=100)# no. of bootstraps
res.boot$t0 # original estimates
res.boot$t # all the bootstrap estimates
# Example to find all confidence intervals
my_stat <- function(x, ind) {stat(x[ind])}
# Confidence intervals for variable i
boot.ci(res.boot, type= Look in red, index=i)
# Intervals by hand (t0: estimate, t: bootstrapped)
quantile.CI <- quantile(t,probs=c(0.025,0.975))
norm<-c(t0-qnorm(0.975)*sd(t),t0+qnorm(0.975)*sd(t))
reversed.CI <- t0-quantile(t-t0,probs=c(0.975,0.025))
\end{codebox}